---
title: "simpleRegress"
author: "Michelle Coleman"
date: "April 11, 2021"
output:
    html_document:
     toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bears regression model

setup regression models

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

# NECK
## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
new <- data.frame(NECK=bears$NECK[c(5,15,23)])
predict(simp, new, se.fit=TRUE)
```


# HEADWTH
## Model LENGTH ~ HEADWTH 


```{r}
simpHW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```

```{r}
new <- data.frame(HEADWTH=bears$HEADWTH[c(5,15,23)])
predict(simpHW, new, se.fit=TRUE)
```

# HEADLEN
## Model LENGTH - HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(5, 15, 23)])
predict(simpHL, new, se.fit=TRUE)
```

# WEIGHT
## Model LENGTH - WEIGHT

```{r}
simpW <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpW)
summary.lm(simpW)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpW, new, se.fit=TRUE)
```

# CHEST
## Model LENTGH - CHEST

```{r}
simpC <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpC)
summary.lm(simpC)
```

```{r}
new <- data.frame(CHEST=bears$CHEST[c(5, 15, 23)])
predict(simpC, new, se.fit=TRUE)
```

# CONCLUSION


The best model was HEADLEN as seen by the adjusted R-squared the prediction of the length for bears 5, 15 and 23 is
70.31 51.94 58.83


The actual lengths of the was
`r bears$LENGTH[c(5, 15, 23)]`.


The error in prediction for bear number 5 is about 8 inches, for bear number 15 the prediction is right on, for bear number 23 the error and prediction was just under six inches.


















